Highlighting Disputed Information on the Web

### 2009-10-26 papers/www_disputefinder/disputefinder.tex
More improvements to the system section

Dispute Finder consists of a database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to recognise them when they appear on a web page. The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

@@

\subsection{Recognizing Textual Entailment}

@@

One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it condradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical. Dispute Finder thus instead uses separate approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims. Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.

@@

@@

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{claimview}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selecting "use as evidence" from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

@@

One of the key challenges for Dispute Finder is determining what claims are Disputed. Dispute Finder takes the approach of maintaining a database of known disputed claims, which it then looks for on web pages.

What we are after is not a list of everything that has every been disputed by anyone, but a list of claims that are frequently believed and are opposed by reliable sources. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/add_claim.png}
	\caption{Interface for adding a new disputed claim}
	\label{add_claim}
	\end{center}
\end{figure}

Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them. For example Snopes.com maintains a list of urban legends and politifact.com maintains a list of false claims about politics. We automatically import all claims that these sites debunk into our database and treat the sites themselves as reliable sources about the claims they debunk. In the future we intend to also import claims from other such sites.

We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{web-add?}). The web interface is modeled after common issue-reporting software such as UserVoice\footnote{url?}. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing source.

>>>>

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/snippet_claim_article_fancy2.png}
	\caption{Snippets entail claims, which are entailed or contradicted by articles}
	\label{snippet_claim_article}
	\end{center}
\end{figure}

Dispute Finder consists of a database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_clim_article}). The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

@@

\subsection{Recognizing Textual Entailment}
\label{related:entailment}

@@

One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it condradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical. Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims. Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
	\caption{Article List interface for a disputed claim}
	\label{article_list}
	\end{center}
\end{figure}

@@

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selecting "use as evidence" from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

@@

One of the biggest challenges in Dispute Finder, is how to build a list of disputed claims that should be highlighted for users. As discussed in Section~\ref{related:entailment}, rather than directly inferring whether a snippet is disputed by a trusted article on the web, Dispute Finder instead builds a database of known disputed claims and tries to determine whether a snippet on a web page entails the truth of one of these claims.

\todo{We are repeating information between here and the related work section on Recognizing Textual Entailment}

We do not want the database of disputed claims to contain everything that has every been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/add_claim_list.png}
	\caption{Interface for adding a new disputed claim manually}
	\label{add_claim}
	\end{center}
\end{figure}

Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them. For example Snopes.com maintains a list of urban legends and Politifact.com maintains a list of false claims about politics. We automatically import all claims that either of these sites debunk into our database and treat the sites themselves as reliable sources about the claims they debunk. In the future we intend to also import claims from other such sites, and allow users to choose which feeds of disputed claims should be used to highlight snippets on pages they browse.

We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{add_claim}). The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.

The automatic import feeds allow Dispute Finder to bootstrap a large database of disputed claims without needing a large active user community and the crowdsourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.

\todo{Say how many disputed claims}

\todo{talk about duplicates}
